%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
{Software Developer} % Job title
{DF/Net Software} % Organization
{Dundas, Canada} % Location
{Jan. 2018 - Present} % Date(s)
{I am a core member in the software development team that is responsible for creating a Clinical Trials Data Management System. I have led DFweb development, the web solution in DFdiscover suite. I designed the software architecture for DFweb, developed numerious features - data collection ability, query function, document management, and edit checks, built the next generation of our product, used by over 8000 users. I presented in DFUG 2018 to exhibit DFweb and then made the first release of DFweb. I wrote DFweb user guide documentation. DFweb is mainly developed using AngularJS, Angular 8, HTML5, CSS, Bootstrap 3, Web Assembly, and Restful API.
}

  \cventry
{Research Assistant} % Job title
{McMaster University} % Organization
{Hamilton, Canada} % Location
{July. 2017 - Nov. 2017} % Date(s)
{My responsibility is to design a web-based visualization platform for Canarie Intrusion Detection System, which uses a PAC (Presentation-Abstraction-Control) software design architecture. I use Node.js as the backend, Angular, HTML5, CSS3 and Material Design Lite as the frontend, and Elastic stack (File beat, Logstash, Elasticsearch, Kibana, TLS connection, RabbitMQ) as the database search solution. Log source files come from the Bro Intrusion Detection System. 
	%      \begin{cvitems} % Description(s) of tasks/responsibilities
	%        \item {SFWR ENG 4J03: Communications Systems}
	%        \item {SFWR ENG 3MX3: Signals and Systems}
	%        \item {SFWR ENG 4AA4: Real-Time Systems and Control Applications}
	%        \item {MECHTRON 4AA4: Real-Time Systems and Control Applications}
	%        \item {COMP SCI 3SD3: Concurrent Systems}
	%        \item {MECHTRON 3DX4:  Dynamic Models and Control of Physical Systems}
	%        \item {MECHTRON 3TB4: Embedded Systems Design II}
	%      \end{cvitems}
}

%  \cventry
%    {Teaching Assistant} % Job title
%    {McMaster University} % Organization
%    {Hamilton, Canada} % Location
%    {Jan. 2016 - Apr. 2017} % Date(s)
 %   {Courses taught: Communications Systems, Signals and Systems, Real-Time Systems and Control Applications, Concurrent Systems, Dynamic Models and Control of Physical Systems, and Embedded Systems Design II
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {SFWR ENG 4J03: Communications Systems}
%        \item {SFWR ENG 3MX3: Signals and Systems}
%        \item {SFWR ENG 4AA4: Real-Time Systems and Control Applications}
%        \item {MECHTRON 4AA4: Real-Time Systems and Control Applications}
%        \item {COMP SCI 3SD3: Concurrent Systems}
%        \item {MECHTRON 3DX4:  Dynamic Models and Control of Physical Systems}
%        \item {MECHTRON 3TB4: Embedded Systems Design II}
%      \end{cvitems}
%    }





%---------------------------------------------------------
\end{cventries}
